The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
rm, mv comments

Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales. Habitat selection is often
measured using resource selection functions (RSFs) and species distribution
models (SDMs). Both of these methods are based on the proportion of used
resources and available resources for an animal. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, (3) the habitat patches within the home range and
(4) specific resources within a habitat patch. Extending beyond this
hierarchical perspective, Mayor (2009) reviewed scale in habitat selection and

Habitat selection - can be measured by RSFs and importance of scale: 
Scale in habitat selection... Mayor (2019)

Habitat selection is scale dependent and 
*  Johnson (1980)

What new insights will multilayer networks lead to

<!--

Scale + habitat selection and space use
types of scale to consider in these types of ML nets

McGarigal 2016 organisms select habitat at multiple scales, temporal spatial 
should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics

Johnson 1980 1st order = selection of the physical or geographical range of a species
2nd order = selection of a home range of an individual or social group
3rd order = selection of various habitat patches within the home range 
4th order = selection of specific resources within a habitat patch

* Mayor et al. 2009 paper 
* MRSF Laforge paper 
* van Beest et al. 2014 scale paper 
* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
* Multi-scale habitat selection modeling: a review and outlook
-->

Scale in habitat selection... Mayor (2019)

>>>>

<!-- McGarigal 2016 organisms select habitat at multiple scales, temporal spatial 
should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
MRSF Laforge paper 
van Beest et al. 2014 scale paper 
Habitat–performance relationships: finding the right metric at a given spatial scale
Multi-scale habitat selection modeling: a review and outlook
-->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales. Habitat selection is often
measured using resource selection functions (RSFs) and species distribution
models (SDMs). Both of these methods are based on the proportion of used
resources and available resources for an animal. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, (3) the habitat patches within the home range and
(4) specific resources within a habitat patch. Extending beyond this
hierarchical perspective, Mayor (2009) reviewed scale in habitat selection and
